Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-06-27 Paper/Figures.Rnw

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	  geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), data=spans, size=.375) + 
    	  geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), data=spans, size=.375) + 
    	  geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans, size=.375) + 
    	  geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype="11", data=thresholds, size=.375) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype="11", data=thresholds, size=.375) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.end), data=thresholds, shape=18) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.25), limits=c(-0.1, 1.1), expand=c(0, 0)) +
        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
        scale_color_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
        scale_fill_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
        labs(x=NULL, y="Cumulative indicence fraction") + 
        theme(
            panel.grid.major.x=element_blank(),
            panel.grid.minor.x=element_blank(),
            legend.title=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
            legend.position="bottom"
        )

>>>>

    p = ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	  geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), data=spans, size=.375) + 
    	  geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), data=spans, size=.375) + 
    	  geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans, size=.375) + 
    	  geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype="11", data=thresholds, size=.375) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype="11", data=thresholds, size=.375) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.end), data=thresholds, shape=18) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.25), limits=c(-0.1, 1.1), expand=c(0, 0)) +
        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
        scale_color_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
        scale_fill_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
        labs(x=NULL, y="Cumulative indicence fraction") + 
        theme(
            panel.grid.major.x=element_blank(),
            panel.grid.minor.x=element_blank(),
            legend.title=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
            legend.position="bottom"
        )
	p

    dev.off()

    tikz(sprintf("%s/coverageByRegionAAPInsight-Standalone.tex", figuresDir), width=16/3, height=3, pointsize=10, standAlone=TRUE)
	p = p + facet_wrap(~county, ncol=3, labeller=labeller(county=countyLabels))
	p
    dev.off()
@
